Exploring Science Fiction \& Fantasy Q/A

### 2020-02-18 Article_Final/main.tex
s

% -- End of custom LaTeX packages --
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
    }
\usepackage{hyperref}x	
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

@@

% Do not modify the author tag below, just let it be blank
\author{}
\twocolumn
% Fill in assignment abstract
\begin{abstract}
In this assignment we parsed a dataset, in the form of XMLs, through a Hadoop- and pig apache. We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from science fiction and Fantasy stack exchange.

@@

We chose to work together because both of us have python background, choosing python as main programming language. We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.

Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs. Hadoop provides a framework which allow users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience. Pig is a MapReduce abstraction, working on Hadoop methods, that we use in some tasks due to its efficiency. We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both show our ability to employ both methods and get experience with the two methods.

\section{Main functions}
The datasets consists only XML files which, being of a document-oriented database, is structured into attributes attributed to each element of the file. Being oriented towards use in HTML, i.e. a website, the attributes contain ASCII characters, punctuation, numbers and HTML tags that we don't want to be there. For this we designed the function cleanBody, meant to clean the text gained from the XML-documents. Additionally a function to parse the XML files was required, for which we created xmlparser. Lastly, we created a general function that would perform the duties of putting out the results of the mapper function; mapper\_core. This section explains their implementations, details the modules imported and describes the bash-script used to run our python-scripts: 
\subsection{\emph{cleanBody}}
The cleanBody function formats strings to be parseable by python interpreters. The function removes case sensitivity, ascii characters, HTML formatting, and treats anything separated by blanked space or / as separated words. This simple implementation of text formatting will affect the results of some tasks. For instances the name "Jens-Petter" will be interpreted as the word "jenspetter" and the filepath /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension".
The function takes a string as input, formats it and outputs a list of all the words split by the string.split(" ") function.
It uses the sub-function of the open source re module to remove HTML-tags and ASCII function that is inherent starting with in Python 3 to convert all characters to parse-able ASCII text. The symbols in ignore\_char, which are characters we are not considering is defined by the builtin string functions string.punctuation and string.digits.
\begin{lstlisting}[language=Python, caption=cleanBody function]
def cleanBody(body):
    body = body.lower()
    body = ascii(body)
    body = sub("<.+?>","",body)
    body = body.replace("/", " ")
    body = body.strip()

@@

\begin{itemize}
  \item Single: Assumes input "words" is a list of words to print. Prints word in words as (word, 1). Ignores empty strings and spaces.
  \item Double: Assumes input "words" is two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
  \item Triple: Assumes input "words" is three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
\end{itemize}

@@

\subsection{\emph{XML Parser}}
The XML Parser function parses an xml using the open-source xml.etree.ElementTree. For normal use it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
Although parsing an entire XML-file takes up significant memory, this method fits our dataset. It has been separated out as a function so it may be easily replaced by other methods more fit for large files. The input for this function is a XML-file and the output is a parsed XML-file.

@@

\subsection{\emph{Import xml.etree.ElementTree}}
ElementTree is a part of the xml open-source library. XML is an inherently hierarchical data format, being document-oriented, and is naturally represented using a tree-like structure. By using the library ElementTree will represent the XML document as a tree, and elements of the tree is represented as single nodes. 
\begin{lstlisting}[language=Python, caption=Import for ElementTree]
import xml.etree.ElementTree as ET
\end{lstlisting}

@@

\subsection{\emph{Bash-script}}
As an example of files being run, this bash-script that was used while testing out scripts is provided. It was used on a windows PC, meaning scripts had to be converted to unix code. It automatically names, cleans, and saves outputs locally. Below is the base bash-script used for the tasks. The three variables taskNumber, taskName and sourceFile are used to operate it. The bash-scripts for the tasks containing Pig-scripts have an additional clause for the purpose of running the Pig-script.
\lstinputlisting[title=Bash-script for a windows-based environment]{Code_output/runBasis_windows.sh}

\subsection{\emph{Data trimming}}
We use the environment Docker to act as a data cluster. Files that are bigger than 128MB  are not readable by the module we use to parse XMLs within the Docker environment (whether this is due to this being the standard size of a datablock we were not able to tell). Between the choice of running our software outside Docker and trimming the files for data, we elected to trim the relevant file for this case: Posts.xml. We deleted lines 74 699 through 171 247 and used the remaining data as a basis for out analysis.

% --TASK1--
\section{Task 1 \emph{Warmup}}
%This part of the task is about get to know how hadoop- and pig apache works and how to parse XML  files throught python code. 
\subsection{\emph{WordCount}}
\textbf{Assumption}: Count the words in body of questions, identified by PostTypeID="1", in \textit{Posts.xml}. The result should be a list of each word and how many times it occurs in the bodies of questions. \\ \\
\textbf{Implementation}: The mapper uses the xmlparser function to parse an XML-file, iterates through all rows in parsed file, cleans text using the cleanBody function and prints output for the reducer script by using the mapper\_core function.
The reducer receives the mapper output, parses it and iterates through the parsed lines. A counter variable is used to track repeated words, outputting the word with the counter when the word stops repeating. \\ \\
\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things as words that clearly are not. See line 2 in 1a\_output for example; what is possibly an "accordingly" followed by three lineskips and then an "in" is interpreted as "accordinglynnnin" and is counted as a word. \\

@@

\subsection{\emph{Pig top 10}}
\textbf{Assumption}: Write a pig script to select top 10 listed words after removing the stopwords from \textit{Posts.xml}. The output should be a list of the top 10 listed words and the corresponding occurrence count.\\ \\
\textbf{Implementation}: Given this task being based on 1d StopWords, the mapper and reducer are the same for both tasks. Our pig loaded the output from the MapReduce job, ordered it by count, limited it to 10 elements and stored it into a text file: 1ePig\_Output.txt. \\ \\
\textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an hdfs cluster as opposed to a local storage location.
\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{Code_output/output1e.txt}

\subsection{\emph{Tags}}
\textbf{Assumption}: Write a MapReduce job to create a dictionary over unique tags in \textit{Posts.xml}. The result should be a list of unique tags.\\ \\
\textbf{Implementation}: This MapReduce job functions similarly to 1a WordCount, except it has to be aware of whether the post has a tag at all or not, being implemented when tags are extracted from the row. \\ \\
\textbf{Notes/Reflection}: The tags are separated by chevrons, and would be fused by cleanBody, so we elected to replace them with spaces. Some of the posts lacked any tag attribute, so we elected to pass over those.
\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{Code_output/output1f.txt}

@@

\subsection{\emph{Top users}}
\textbf{Assumption}:Write a pig script or MapReduce job to find top 10 users based on Reputation attribute in \textit{Users.xml}. The result should be a list of the 10 users based with the highest reputation value. \\ \\
\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out name and the reputation attribute. Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to it looping through its inputs. The reducer is the same as the reducer of 2b Unique users. The pig script functions the same way as in 1e Pig Top 10\\ \\
\textbf{Notes/Reflection}: We elected here to use pig to order the MapReduce output in order to get experience.
\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{Code_output/output2c.txt}

@@

\subsection{\emph{Countries}}
\textbf{Assumption}: Write a MapReduce job to count the amount of users attributed to a country by the Location attribute in \textit{Users.xml}. The result should be a list of different countries and corresponding users. \\ \\
\textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator, since spaces are part of location. If Location is separated by a \',\' the last part is treated as the country. \\ \\
\textbf{Notes/Reflection}: Because by our judgement locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator. Anything after the last \',\' is treated as a country. A location with no \',\' is treated as a country. Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{Code_output/output2g.txt}

\subsection{\emph{Names}}
\textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list top 10 common names. \\ \\
\textbf{Implementation}: This mapper functions similarly to 2g Countries, except it extracts the DisplayName-attribute in place of the Location-attribute. The reducer functions similarly to 2d Top questions, except it parses differently and has different text formatting for the output due to the decrease from 3 to 2 arguments \\ \\
\textbf{Notes/Reflection}: Here the most common name is User. This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3 etc. The task suggested explicitly that we should split up names by spaces, perhaps wanting to separate out last names from first names. Due to the nature of Displaynames usually not being full legal names, we have elected to interpret a "name" as the full name given in DisplayName.
\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{Code_output/output2h.txt}

@@

\subsection{\emph{Bigram}}
\textbf{Assumption}: We chose to write a MapReduce job to find the most common pair of adjacent words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}. A bigram is a combination of two words in a sequence. For instance the sentence "Big data is big" contains the bigrams "Big data", "data is", and "is big". The result should be the most common bigram along with a count of how many times it occurs. \\ \\
\textbf{Implementation}: This MapReduce is exactly the same as 1a WordCount, except we output each bigram in the body instead of each word. Because of this we he had to forego the mapper\_core for a print function inside a loop looping through every bigram. The reducer finds the most common bigram by iteratively comparing each elements second element (the bigrams count) against a variable declared maximum. \\ \\
\textbf{Notes/Reflection}: In the print-loop we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{Code_output/output3a.txt}

@@

% --TASK4--
\section{Task 4 \emph{Search engine}}
\subsection{\emph{Title index}}
\textbf{Assumption}: Write MapReduce job to create index over titles, bodies and answers of questions in \textit{Posts.xml}. The result should be a simple index that lists posts words appear in by their Id's. \\ \\
\textbf{Implementation}: This mapper function parses through all rows in posts.xml. It then forks over whether PostTypeId is 1 or 2, i.e. whether it is an answer or question, extracting the relevant id, body and title from the row. It contains a combiner to speed up the process, removing duplicates. The reducer parses the input and iterates through all the lines. It uses two variables to know what the last word and associated Id was, skipping the word if both are the same, adding the Id to a list if \textit{only} the word is the same, and putting out the word with an associated list of Id's if neither is the same, i.e. it has finished working with the word. \\ \\
\textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary, since we are working with small file-sizes.
\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{Code_output/output4.txt}

\section{Conclusion}
Through this assignment we gained experience in using MapReduce jobs and pig scripts. We parsed XML-documents and extracted specific information we were looking for to be formatted to an output to each tasks.

>>>>

% -- End of custom LaTeX packages --
\lstdefinestyle{mystyle}{
  backgroundcolor=\color{backcolour},  
  commentstyle=\color{codegreen},
  keywordstyle=\color{magenta},
  numberstyle=\tiny\color{codegray},
  stringstyle=\color{codepurple},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,     
  breaklines=true,         
  captionpos=b,           
  keepspaces=true,         
  numbers=left,         
  numbersep=5pt,          
  showspaces=false,         
  showstringspaces=false,
  showtabs=false,          
  tabsize=2
  }
\usepackage{hyperref}	
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,    
  urlcolor=cyan,
}
\urlstyle{same}

@@

% Do not modify the author tag below, just let it be blank
\author{}
\twocolumn
% Fill in assignment abstract
\begin{abstract}
In this assignment, we parsed through datasets, in the form of XMLs, through a Hadoop- and pig apache. We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from Science Fiction and Fantasy Q/A stack exchange.

@@

We chose to work together because both of us have python background, choosing python as the main programming language. We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.

Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs. Hadoop provides a framework that allows users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience. Pig is a MapReduce abstraction, working on Hadoop methods, that we use in some tasks due to its efficiency. We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both shows our ability to employ both methods and get experience with the two methods.

\section{Main functions}
The datasets consist only XML files which, being of a document-oriented database, is structured into attributes attributed to each element of the file. Being oriented towards use in HTML, i.e. a website, the attributes contain ASCII characters, punctuation, numbers and HTML tags that we don't want to be there. For this, we designed the function cleanBody, meant to clean the text gained from the XML-documents. Additionally, a function to parse the XML files was required, for which we created xmlparser. Lastly, we created a general function that would perform the duties of putting out the results of the mapper function; mapper\_core. This section explains their implementations, details the modules imported and describes the bash-script used to run our python-scripts: 
\subsection{\emph{cleanBody}}
The cleanBody function formats strings to be parseable by python interpreters. The function removes case sensitivity, ASCII characters, HTML formatting, and treats anything separated by blanked space or / as separated words. This simple implementation of text formatting will affect the results of some tasks. For instance, the name "Jens-Petter" will be interpreted as the word "jenspetter" and the file path /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension".
The function takes a string as input, formats it and outputs a list of all the words split by the string.split(" ") function.
It uses the sub-function of the open source re module to remove HTML-tags and ASCII function that is inherent starting with in Python 3 to convert all characters to parse-able ASCII text. The symbols in ignore\_char, which are characters we are not considering is defined by the builtin string functions string.punctuation and string.digits.
\begin{lstlisting}[language=Python, caption=cleanBody function]
def cleanBody(body):
  body = body.lower()
  body = ascii(body)
  body = sub("<.+?>","",body)
  body = body.replace("/", " ")
  body = body.strip()

@@

\begin{itemize}
 \item Single: Assumes input "words" is a list of words to print. Prints word in words as (word, 1). Ignores empty strings and spaces.
 \item Double: Assumes input "words" are two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
 \item Triple: Assumes input "words" is three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
\end{itemize}

@@

\subsection{\emph{XML Parser}}
The XML Parser function parses an XML using the open-source xml.etree.ElementTree. For normal use, it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
Although parsing an entire XML-file takes up significant memory, this method fits our dataset. It has been separated out as a function so it may be easily replaced by other methods more fit for large files. The input for this function is an XML-file and the output is a parsed XML-file.

@@

\subsection{\emph{Import xml.etree.ElementTree}}
ElementTree is a part of the XML open-source library. XML is an inherently hierarchical data format, being document-oriented, and is naturally represented using a tree-like structure. By using the library ElementTree will represent the XML document as a tree, and elements of the tree is represented as single nodes. 
\begin{lstlisting}[language=Python, caption=Import for ElementTree]
import xml.etree.ElementTree as ET
\end{lstlisting}

@@

\subsection{\emph{Bash-script}}
As an example of files being run, this bash-script that was used while testing out scripts is provided. It was used on a Windows PC, meaning scripts had to be converted to Unix code. It automatically names, cleans and saves outputs locally. Below is the base bash-script used for the tasks. The three variables taskNumber, taskName, and sourceFile are used to operate it. The bash-scripts for the tasks containing Pig-scripts have an additional clause for running the Pig-script.
\lstinputlisting[title=Bash-script for a windows-based environment]{Code_output/runBasis_windows.sh}

\subsection{\emph{Data trimming}}
We use the environment Docker, to act as a data cluster. Files that are bigger than 128MB are not readable by the module we use to parse XMLs within the Docker environment (whether this is due to this being the standard size of a data block we were not able to tell). Between the choice of running our software outside Docker and trimming the files for data, we elected to trim the relevant file for this case: Posts.xml. We deleted lines 74 699 through 171 247 and used the remaining data as a basis for our analysis.

% --TASK1--
\section{Task 1 \emph{Warmup}}
%This part of the task is about to get to know how Hadoop- and Pig apache works and how to parse XML files through python code. 
\subsection{\emph{WordCount}}
\textbf{Assumption}: Count the words in body of questions, identified by PostTypeID="1", in \textit{Posts.xml}. The result should be a list of each word and how many times it occurs in the bodies of questions. \\ \\
\textbf{Implementation}: The mapper uses the xmlparser function to parse an XML-file, iterates through all rows in the parsed file, cleans text using the cleanBody function and prints output for the reducer script by using the mapper\_core function.
The reducer receives the mapper output, parses it and iterates through the parsed lines. A counter variable is used to track repeated words, outputting the word with the counter when the word stops repeating. \\ \\
\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things like words that are not. See line 2 in 1a\_output for example; what is possibly an "accordingly" followed by three line skips and then an "in" is interpreted as "accordinglynnnin" and is counted as a word. \\

@@

\subsection{\emph{Pig top 10}}
\textbf{Assumption}: Write a pig script to select the top 10 listed words after removing the stopwords from \textit{Posts.xml}. The output should be a list of the top 10 listed words and the corresponding occurrence count.\\ \\
\textbf{Implementation}: Given this task being based on 1d StopWords, the mapper and reducer are the same for both tasks. Our pig loaded the output from the MapReduce job, ordered it by count, limited it to 10 elements and stored it into a text file: 1ePig\_Output.txt. \\ \\
\textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an HDFS cluster as opposed to a local storage location.
\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{Code_output/output1e.txt}

\subsection{\emph{Tags}}
\textbf{Assumption}: Write a MapReduce job to create a dictionary over unique tags in \textit{Posts.xml}. The result should be a list of unique tags.\\ \\
\textbf{Implementation}: This MapReduce job functions similarly to 1a WordCount, except it has to be aware of whether the post has a tag at all or not, being implemented when tags are extracted from the row. \\ \\
\textbf{Notes/Reflection}: The tags are separated by chevrons and would be fused by cleanBody, so we elected to replace them with spaces. Some of the posts lacked any tag attribute, so we elected to pass over those.
\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{Code_output/output1f.txt}

@@

\subsection{\emph{Top users}}
\textbf{Assumption}: Write a pig script or MapReduce job to find the top 10 users based on the Reputation attribute in \textit{Users.xml}. The result should be a list of the 10 users based on the highest reputation value. \\ \\
\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out a name and the reputation attribute. Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to its looping through its inputs. The reducer is the same as the reducer of 2b Unique users. The pig script functions the same way as in 1e Pig Top 10\\ \\
\textbf{Notes/Reflection}: We elected here to use Pig-script to order the MapReduce output to get experience.
\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{Code_output/output2c.txt}

@@

\subsection{\emph{Countries}}
\textbf{Assumption}: Write a MapReduce job to count the amount of users attributed to a country by the Location attribute in \textit{Users.xml}. The result should be a list of different countries and corresponding users. \\ \\
\textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator since spaces are part of the location. If Location is separated by a \',\' the last part is treated as the country. \\ \\
\textbf{Notes/Reflection}: Because by our judgment locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator. Anything after the last \',\' is treated as a country. A location with no \',\' is treated as a country. Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{Code_output/output2g.txt}

\subsection{\emph{Names}}
\textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list of top 10 common names. \\ \\
\textbf{Implementation}: This mapper functions similarly to 2g Countries, except it extracts the DisplayName-attribute in place of the Location-attribute. The reducer functions similarly to 2d Top questions, except it parses differently and has different text formatting for the output due to the decrease from 3 to 2 arguments \\ \\
\textbf{Notes/Reflection}: Here the most common name is User. This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3, etc. The task suggested explicitly that we should split up names by spaces, perhaps wanting to separate out last names from first names. Due to the nature of Displaynames usually not being full legal names, we have elected to interpret a "name" as the full name given in DisplayName.
\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{Code_output/output2h.txt}

@@

\subsection{\emph{Bigram}}
\textbf{Assumption}: We chose to write a MapReduce job to find the most common pair of adjacent words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}. A bigram is a combination of two words in a sequence. For instance the sentence "Big data is big" contains the bigrams "Big data", "data is", and "is big". The result should be the most common bigram along with a count of how many times it occurs. \\ \\
\textbf{Implementation}: This MapReduce is the same as 1a WordCount, except we output each bigram in the body instead of each word. Because of this we he had to forego the mapper\_core for a print function inside a loop looping through every bigram. The reducer finds the most common bigram by iteratively comparing each elements second element (the bigrams count) against a variable declared maximum. \\ \\
\textbf{Notes/Reflection}: In the print-loop, we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{Code_output/output3a.txt}

@@

% --TASK4--
\section{Task 4 \emph{Search engine}}
\subsection{\emph{Title index}}
\textbf{Assumption}: Write MapReduce job to create an index over titles, bodies, and answers of questions in \textit{Posts.xml}. The result should be a simple index that lists posts words appear in by their Id's. \\ \\
\textbf{Implementation}: This mapper function parses through all rows in posts.xml. It then forks over whether PostTypeId is 1 or 2, i.e. whether it is an answer or question, extracting the relevant id, body, and title from the row. It contains a combiner to speed up the process, removing duplicates. The reducer parses the input and iterates through all the lines. It uses two variables to know what the last word and associated Id was, skipping the word if both are the same, adding the Id to a list if \textit{only} the word is the same, and putting out the word with an associated list of Id's if neither is the same, i.e. it has finished working with the word. \\ \\
\textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary since we are working with small file-sizes.
\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{Code_output/output4.txt}

\section{Conclusion}
Through this assignment, we gained experience in using MapReduce jobs and pig scripts. We parsed XML-documents and extracted specific information we were looking for to be formatted to output to each task.
